### 2022-04-19 Paper.tex
Signature Work paper init commit

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
\usepackage{unicode-math}
\defaultfontfeatures{Scale=MatchLowercase}
\defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
    \usepackage[]{microtype}
    \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
    \IfFileExists{parskip.sty}{%
        \usepackage{parskip}
    }{% else
        \setlength{\parindent}{0pt}
        \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
    \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
    hidelinks,
    pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
    \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
\usepackage{selnolig}  % disable illegal ligatures
\fi

\author{}
\date{}

\begin{document}

    \textbf{Duke Kunshan University}

    \textbf{Division of Natural and Applied Sciences}

    \textbf{SW theses - Template}

    Instructions

    \begin{itemize}
        \item
        Black text -- \emph{Do not delete}. Everything in black stays in the
        document.
        \item
        Red text -- \emph{Model text}. Replace with your own text, then change
        the ink color to black.
        \item
        Blue text -- \emph{Delete}. The blue text is instructional, providing
        general guidance for what goes into a particular section.
    \end{itemize}

    \textbf{Overview}

    The Title Page, Table of Contents, and Abstract, are the first three
    pages of the document. The Table of Contents as (iiI), and the Abstract
    as (ii). (The title page does not include a page number). You should
    include a single-page Acknowledgements/Dedication and/or Appendix/ces as
    options. The acknowledgements, or dedication, page is should be the
    second page, numbered (iii), with the Table of Contents becoming (iv).
    The appendix/ces or supplemental content pages should follow the
    source/works cited. The appendix or supplemental content pages should
    continue with the Arabic numbering. All page numbers must be bottom
    centered. See next section for an example outline of the document.

    Title page

    \begin{itemize}
        \item
        Title written in ALL CAPS
        \item
        The title is centered at the top of the page
        \item
        The title cannot exceed three lines
        \item
        The word `by' is on its own line
        \item
        Your name should be capitalized in its regular way
        \item
        The phrases `Signature Work submitted for' are to remain as is
        \item
        Enter the date of submission with normal capitalization as Month, Day,
        Year
    \end{itemize}

    Table of Contents

    \begin{itemize}
        \item
        The table of contents should be left justified, each chapter should be
        noted, including the page number.
    \end{itemize}

    \textbf{REMEMBER TO DELETE THIS PAGE BEFORE SUBMISSION}

    THESIS TITLE THAT EXTENDS OVER ONE LINE GOES IN INVERTED PYRAMID FORM

    by

    First Name\_Last Name

    Signature Work Product, in partial fulfilment of the Duke Kunshan
    University Undergraduate Degree Program

    \emph{\{Enter date of submission with normal capitalization as Month,
        Day, Year\}}

    Signature Work Program

    Duke Kunshan University

    APPROVALS

    \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

    \emph{Mentor: First Name, Last Name and Division (without abbreviations)
        using normal capitalization}

    \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

    Marcia B. France, Dean of Undergraduate Studies

    \protect\hypertarget{_Toc93021168}{}{}\textbf{ABSTRACT} \emph{(in
    English)}

    \emph{150 -- 200 words}. \emph{An abstract is a brief statement of the
    problem or the purpose of the research. It should indicate the
    theoretical work or experimental plan used, summarize principal findings
    of the research, and point out major conclusions. Appropriate safety
    information should be included when applicable. This should be the
    section you write last to be sure that it accurately reflects the
    content of the document.}

    \protect\hypertarget{_Toc93021169}{}{}\textbf{ABSTRACT} \emph{(in
    Chinese)}

    150 - 200
    字。摘要是对问题或研究目的的简要说明。说明所使用的理论工作或实验计划，总结研究的主要发现，并指出主要结论。适用时应包括适当的安全信息。这应该是您最后编写的部分，以确保它准确反映文档的内容。

    150 - 200 Zì. Zhāiyào shi duì wèntí huò yánjiū mùdì de jiǎnyào shuōmíng.
    Shuōmíng suǒ shǐyòng de lǐlùn gōngzuò huò shíyàn jìhuà, zǒngjié yánjiū
    de zhǔyào fāxiàn, bìng zhǐchū zhǔyào jiélùn. Shìyòng shí yīng bāokuò
    shìdàng de ānquán xìnxī. Zhè yīnggāi shì nín zuìhòu biānxiě de bùfèn, yǐ
    quèbǎo tā zhǔnquè fǎnyìng wéndàng de nèiróng.

    \hypertarget{acknowledgements}{%

        \section{ACKNOWLEDGEMENTS}\label{acknowledgements}}

    \emph{Individuals and organizations who helped with the research project
    and provided financing are thanked in a paragraph of the thesis. Do not
    include individual titles in the acknowledgments. However, it is
    appropriate to state grant numbers and sponsors. Examples would like
    SELF, SRS, SW Grants, etc.}

    \hypertarget{table-of-content}{%

        \section{TABLE OF CONTENT}\label{table-of-content}}

    \hypertarget{section}{%

        \section{}\label{section}}

    \protect\hyperlink{_Toc93021168}{\textbf{ABSTRACT 3}}

    \protect\hyperlink{_Toc93021169}{\textbf{ABSTRACT 3}}

    \protect\hyperlink{acknowledgements}{\textbf{ACKNOWLEDGEMENTS 4}}

    \protect\hyperlink{table-of-content}{\textbf{TABLE OF CONTENT 5}}

    \protect\hyperlink{list-of-tables}{\textbf{LIST OF TABLES 6}}

    \protect\hyperlink{table-of-figures}{\textbf{TABLE OF FIGURES 7}}

    \protect\hyperlink{section-1}{\textbf{INTRODUCTION 8}}

    \protect\hyperlink{material-and-methods}{\textbf{MATERIAL AND METHODS
    9}}

    \protect\hyperlink{results}{\textbf{RESULTS 10}}

    \protect\hyperlink{discussion}{\textbf{DISCUSSION 11}}

    \protect\hyperlink{conclusions}{\textbf{CONCLUSIONS 12}}

    \protect\hyperlink{references}{\textbf{REFERENCES 13}}

    \protect\hyperlink{appendices}{\textbf{APPENDICES 14}}

    \protect\hyperlink{_Toc93021181}{\textbf{APPENDIX A: 15}}

    \hypertarget{list-of-tables}{%

        \section{LIST OF TABLES}\label{list-of-tables}}

    \protect\hyperlink{_Toc93020061}{Table 1 Parameters for the optimization
    of the principal component analysis for olive oil adulteration 10}

    \emph{First add captions to your Tables. Right-click on the text above
    and select Update Field to update this list. Word then searches the
    document for your captions and automatically adds a list of tables,
        sorted by page number. The captions must be formatted as in the DNAS SW
        Style Guide}.

    \hypertarget{table-of-figures}{%

        \section{TABLE OF FIGURES}\label{table-of-figures}}

    \protect\hyperlink{_Toc93020444}{Figure 1 The notorious BTC (Brandon the
    Cat) 10}

    \emph{First add captions to your figures. Right-click on the text above
    and select Update Field to update this list. Word then searches the
    document for your captions and automatically adds a list of figures,
        sorted by page number. The captions must be formatted as in the DNAS SW
        Style Guide}.

    \hypertarget{section-1}{%

        \section{}\label{section-1}}

    \hypertarget{introduction}{%

        \section{INTRODUCTION}\label{introduction}}

    \emph{This section includes a clear statement of the problem and the
    reasons for studying it.~Provide a detailed yet concise background
    discussion of the problem and the significance, scope, and limits of the
    work. Outline what has been done previously by citing truly pertinent
    literature but do not include a general survey of semi-relevant
    literature.~ State how your work differs from earlier work in the field
    and demonstrate the continuity from the previous work to your own.}

    \hypertarget{material-and-methods}{%

        \section{MATERIAL AND METHODS}\label{material-and-methods}}

    \emph{This section is obviously discipline specific so use the
    nomenclature that is common for your discipline. However, this section
    should provide sufficient detail about the materials and the methods
    used so that other experienced workers can repeat the experiment and
    obtain comparable results. Cite the appropriate literature when using a
    standard method or protocol and give only the details needed. Identify
    the materials used in the research. For example, computer systems used,
        mathematical theorems exploited, etc.; give information on the purity of
        all chemicals and reagents employed in the research; include the
        chemical/biological names of all compounds and chemical formulas of
        substances that are new or uncommon. Use standard systematic
        nomenclature to unambiguously define well-established compounds,
        processes, equipment, etc.}

    \hypertarget{results}{%

        \section{RESULTS}\label{results}}

    \emph{Summarize the data collected in this section, and their
    statistical treatment. Include only relevant data, but give sufficient
    detail to justify the conclusions.~ It is appropriate in this section to
    use equations, figures, and tables to display your data. Extensive, but
    relevant data, should be reserved for an appendix where it is identified
    as supporting information.}

    \emph{The table or figure must follow as closely as possible after the
    paragraph in which it is referenced. Titles/captions should be kept
    brief.}

    \protect\hypertarget{_Toc93020061}{}{}Table 1 Parameters for the
    optimization of the principal component analysis for olive oil
    adulteration

    \begin{longtable}[]{@{}llll@{}}
        \toprule
        \emph{Replace} & \emph{With} & \emph{Your} & \emph{Table} \\
        \midrule
        \endhead
        &             &             &              \\
        &             &             &              \\
        \bottomrule
    \end{longtable}

    \includegraphics[width=1.95833in,height=1.46875in]{vertopal_23eb081fc9d74a2dbd905a0fc9194429/media/image1.jpeg}\emph{(Replace
    with your figure)}

    \protect\hypertarget{_Toc93020444}{}{}Figure 1 The notorious BTC
    (Brandon the Cat)

    \hypertarget{discussion}{%

        \section{DISCUSSION}\label{discussion}}

    \emph{The discussion section is where you interpret and compare the
    results. The objective is to point out the features and limitations of
    the work. Relate your results to current knowledge in the field and to
    the original purpose for undertaking the project.}

    \hypertarget{conclusions}{%

        \section{CONCLUSIONS}\label{conclusions}}

    \emph{This section is written to put the interpretation of the results
    into the context of the original problem.~ Do not repeat the discussion
    points or include irrelevant material. The conclusion should be based on
    the evidence presented.}

    \hypertarget{references}{%

        \section{REFERENCES}\label{references}}

    \emph{Many bibliographic styles are acceptable for publications in the
    natural sciences. Only for the sake of having one standard across all
    disciplines, you should use this one:}

    \emph{\underline{Body: Superscripted Number}. \{e.g. Nucleotide excision
    repair (NER) is a versatile, error-free mechanism to identify and remove
    a wide assortment of chemically unrelated lesions.\textsuperscript{18}
    NER can be classified into two sub-pathways based on the way DNA lesions
    are identified.\textsuperscript{19} In transcription coupled NER
        (TC-NER), damaged DNA is identified by the stalling of RNA polymerases
        when they encounter bulky covalent DNA lesions.\textsuperscript{20}}

    \emph{\underline{Journal Article}: Evans, D. A., Fitch, D. M., Smith, T.
    E., Cee, V. J. Application of Complex Aldol Reactions to the Total
    Synthesis of Phorboxazole B.~J. Am. Chem.
    Soc.~\textbf{2000,}~122,~10033-10046.}

    \emph{\underline{Book}: Anastas, P. T., Warner, J. C.~Green Chemistry:
    Theory and Practice; Oxford University Press: Oxford, 1998.}

    \hypertarget{appendices}{%

        \section{APPENDICES}\label{appendices}}

    \protect\hypertarget{_Toc93021181}{}{}\textbf{APPENDIX A: APPENDIX
    TITLE}

\end{document}

### 2022-04-21 Paper.tex
Update paper template and remove useless things

@@
 
-    \textbf{SW theses - Template}
-
-    Instructions
-
-    \begin{itemize}
-        \item
-        Black text -- \emph{Do not delete}. Everything in black stays in the
-        document.
-        \item
-        Red text -- \emph{Model text}. Replace with your own text, then change
-        the ink color to black.
-        \item
-        Blue text -- \emph{Delete}. The blue text is instructional, providing
-        general guidance for what goes into a particular section.
-    \end{itemize}
-
-    \textbf{Overview}
-
-    The Title Page, Table of Contents, and Abstract, are the first three
-    pages of the document. The Table of Contents as (iiI), and the Abstract
-    as (ii). (The title page does not include a page number). You should
-    include a single-page Acknowledgements/Dedication and/or Appendix/ces as
-    options. The acknowledgements, or dedication, page is should be the
-    second page, numbered (iii), with the Table of Contents becoming (iv).
-    The appendix/ces or supplemental content pages should follow the
-    source/works cited. The appendix or supplemental content pages should
-    continue with the Arabic numbering. All page numbers must be bottom
-    centered. See next section for an example outline of the document.
-
-    Title page
-
-    \begin{itemize}
-        \item
-        Title written in ALL CAPS
-        \item
-        The title is centered at the top of the page
-        \item
-        The title cannot exceed three lines
-        \item
-        The word `by' is on its own line
-        \item
-        Your name should be capitalized in its regular way
-        \item
-        The phrases `Signature Work submitted for' are to remain as is
-        \item
-        Enter the date of submission with normal capitalization as Month, Day,
-        Year
-    \end{itemize}
-
-    Table of Contents
-
-    \begin{itemize}
-        \item
-        The table of contents should be left justified, each chapter should be
-        noted, including the page number.
-    \end{itemize}
-
-    \textbf{REMEMBER TO DELETE THIS PAGE BEFORE SUBMISSION}
-
     THESIS TITLE THAT EXTENDS OVER ONE LINE GOES IN INVERTED PYRAMID FORM
@@
 
-    First Name\_Last Name
+    Jincheng He
 
@@
 
-    \emph{\{Enter date of submission with normal capitalization as Month,
-        Day, Year\}}
+    \emph{April 21, 2022}
 
@@
 
-    \emph{Mentor: First Name, Last Name and Division (without abbreviations)
-        using normal capitalization}
+    \emph{Mentor: Ming Li, Division of Natural and Applied Sciences}
 
@@
 
-    \protect\hypertarget{_Toc93021168}{}{}\textbf{ABSTRACT} \emph{(in
-    English)}
+    \textbf{ABSTRACT} \emph{(in English)}
 
@@
 
-    \protect\hypertarget{_Toc93021169}{}{}\textbf{ABSTRACT} \emph{(in
-    Chinese)}
+    \textbf{ABSTRACT} \emph{(in Chinese)}
 
@@
 
-    \hypertarget{acknowledgements}{%
+    \section{ACKNOWLEDGEMENTS}\label{acknowledgements}
 
-        \section{ACKNOWLEDGEMENTS}\label{acknowledgements}}
-
-    \emph{Individuals and organizations who helped with the research project
-    and provided financing are thanked in a paragraph of the thesis. Do not
-    include individual titles in the acknowledgments. However, it is
-    appropriate to state grant numbers and sponsors. Examples would like
-    SELF, SRS, SW Grants, etc.}
-
-    \hypertarget{table-of-content}{%
-
-        \section{TABLE OF CONTENT}\label{table-of-content}}
-
-    \hypertarget{section}{%
-
-        \section{}\label{section}}
-
-    \protect\hyperlink{_Toc93021168}{\textbf{ABSTRACT 3}}
-
-    \protect\hyperlink{_Toc93021169}{\textbf{ABSTRACT 3}}
-
-    \protect\hyperlink{acknowledgements}{\textbf{ACKNOWLEDGEMENTS 4}}
-
-    \protect\hyperlink{table-of-content}{\textbf{TABLE OF CONTENT 5}}
-
-    \protect\hyperlink{list-of-tables}{\textbf{LIST OF TABLES 6}}
-
-    \protect\hyperlink{table-of-figures}{\textbf{TABLE OF FIGURES 7}}
-
-    \protect\hyperlink{section-1}{\textbf{INTRODUCTION 8}}
-
-    \protect\hyperlink{material-and-methods}{\textbf{MATERIAL AND METHODS
-    9}}
-
-    \protect\hyperlink{results}{\textbf{RESULTS 10}}
-
-    \protect\hyperlink{discussion}{\textbf{DISCUSSION 11}}
-
-    \protect\hyperlink{conclusions}{\textbf{CONCLUSIONS 12}}
-
-    \protect\hyperlink{references}{\textbf{REFERENCES 13}}
-
-    \protect\hyperlink{appendices}{\textbf{APPENDICES 14}}
-
-    \protect\hyperlink{_Toc93021181}{\textbf{APPENDIX A: 15}}
-
-    \hypertarget{list-of-tables}{%
-
-        \section{LIST OF TABLES}\label{list-of-tables}}
-
-    \protect\hyperlink{_Toc93020061}{Table 1 Parameters for the optimization
-    of the principal component analysis for olive oil adulteration 10}
-
-    \emph{First add captions to your Tables. Right-click on the text above
-    and select Update Field to update this list. Word then searches the
-    document for your captions and automatically adds a list of tables,
-        sorted by page number. The captions must be formatted as in the DNAS SW
-        Style Guide}.
-
-    \hypertarget{table-of-figures}{%
-
-        \section{TABLE OF FIGURES}\label{table-of-figures}}
-
-    \protect\hyperlink{_Toc93020444}{Figure 1 The notorious BTC (Brandon the
-    Cat) 10}
-
-    \emph{First add captions to your figures. Right-click on the text above
-    and select Update Field to update this list. Word then searches the
-    document for your captions and automatically adds a list of figures,
-        sorted by page number. The captions must be formatted as in the DNAS SW
-        Style Guide}.
-
-    \hypertarget{section-1}{%
-
-        \section{}\label{section-1}}
-
-    \hypertarget{introduction}{%
-
-        \section{INTRODUCTION}\label{introduction}}
-
-    \emph{This section includes a clear statement of the problem and the
-    reasons for studying it.~Provide a detailed yet concise background
-    discussion of the problem and the significance, scope, and limits of the
-    work. Outline what has been done previously by citing truly pertinent
-    literature but do not include a general survey of semi-relevant
-    literature.~ State how your work differs from earlier work in the field
-    and demonstrate the continuity from the previous work to your own.}
-
-    \hypertarget{material-and-methods}{%
-
-        \section{MATERIAL AND METHODS}\label{material-and-methods}}
-
-    \emph{This section is obviously discipline specific so use the
-    nomenclature that is common for your discipline. However, this section
-    should provide sufficient detail about the materials and the methods
-    used so that other experienced workers can repeat the experiment and
-    obtain comparable results. Cite the appropriate literature when using a
-    standard method or protocol and give only the details needed. Identify
-    the materials used in the research. For example, computer systems used,
-        mathematical theorems exploited, etc.; give information on the purity of
-        all chemicals and reagents employed in the research; include the
-        chemical/biological names of all compounds and chemical formulas of
-        substances that are new or uncommon. Use standard systematic
-        nomenclature to unambiguously define well-established compounds,
-        processes, equipment, etc.}
-
-    \hypertarget{results}{%
-
-        \section{RESULTS}\label{results}}
-
-    \emph{Summarize the data collected in this section, and their
-    statistical treatment. Include only relevant data, but give sufficient
-    detail to justify the conclusions.~ It is appropriate in this section to
-    use equations, figures, and tables to display your data. Extensive, but
-    relevant data, should be reserved for an appendix where it is identified
-    as supporting information.}
-
-    \emph{The table or figure must follow as closely as possible after the
-    paragraph in which it is referenced. Titles/captions should be kept
-    brief.}
-
-    \protect\hypertarget{_Toc93020061}{}{}Table 1 Parameters for the
-    optimization of the principal component analysis for olive oil
-    adulteration
-
-    \begin{longtable}[]{@{}llll@{}}
-        \toprule
-        \emph{Replace} & \emph{With} & \emph{Your} & \emph{Table} \\
-        \midrule
-        \endhead
-        &             &             &              \\
-        &             &             &              \\
-        \bottomrule
-    \end{longtable}
-
-    \includegraphics[width=1.95833in,height=1.46875in]{vertopal_23eb081fc9d74a2dbd905a0fc9194429/media/image1.jpeg}\emph{(Replace
-    with your figure)}
-
-    \protect\hypertarget{_Toc93020444}{}{}Figure 1 The notorious BTC
-    (Brandon the Cat)
-
-    \hypertarget{discussion}{%
-
-        \section{DISCUSSION}\label{discussion}}
-
-    \emph{The discussion section is where you interpret and compare the
-    results. The objective is to point out the features and limitations of
-    the work. Relate your results to current knowledge in the field and to
-    the original purpose for undertaking the project.}
-
-    \hypertarget{conclusions}{%
-
-        \section{CONCLUSIONS}\label{conclusions}}
-
-    \emph{This section is written to put the interpretation of the results
-    into the context of the original problem.~ Do not repeat the discussion
-    points or include irrelevant material. The conclusion should be based on
-    the evidence presented.}
-
-    \hypertarget{references}{%
-
-        \section{REFERENCES}\label{references}}
-
-    \emph{Many bibliographic styles are acceptable for publications in the
-    natural sciences. Only for the sake of having one standard across all
-    disciplines, you should use this one:}
-
-    \emph{\underline{Body: Superscripted Number}. \{e.g. Nucleotide excision
-    repair (NER) is a versatile, error-free mechanism to identify and remove
-    a wide assortment of chemically unrelated lesions.\textsuperscript{18}
-    NER can be classified into two sub-pathways based on the way DNA lesions
-    are identified.\textsuperscript{19} In transcription coupled NER
-        (TC-NER), damaged DNA is identified by the stalling of RNA polymerases
-        when they encounter bulky covalent DNA lesions.\textsuperscript{20}}
-
-    \emph{\underline{Journal Article}: Evans, D. A., Fitch, D. M., Smith, T.
-    E., Cee, V. J. Application of Complex Aldol Reactions to the Total
-    Synthesis of Phorboxazole B.~J. Am. Chem.
-    Soc.~\textbf{2000,}~122,~10033-10046.}
-
-    \emph{\underline{Book}: Anastas, P. T., Warner, J. C.~Green Chemistry:
-    Theory and Practice; Oxford University Press: Oxford, 1998.}
-
-    \hypertarget{appendices}{%
-
-        \section{APPENDICES}\label{appendices}}
-
-    \protect\hypertarget{_Toc93021181}{}{}\textbf{APPENDIX A: APPENDIX
-    TITLE}
+    \tableofcontents
 

### 2022-04-21 Paper.tex
Add conference paper into signature work paper

@@
 \fi
+\usepackage{stackengine}
 
@@
     150 - 200
-    字。摘要是对问题或研究目的的简要说明。说明所使用的理论工作或实验计划，总结研究的主要发现，并指出主要结论。适用时应包括适当的安全信息。这应该是您最后编写的部分，以确保它准确反映文档的内容。
-
-    150 - 200 Zì. Zhāiyào shi duì wèntí huò yánjiū mùdì de jiǎnyào shuōmíng.
-    Shuōmíng suǒ shǐyòng de lǐlùn gōngzuò huò shíyàn jìhuà, zǒngjié yánjiū
-    de zhǔyào fāxiàn, bìng zhǐchū zhǔyào jiélùn. Shìyòng shí yīng bāokuò
-    shìdàng de ānquán xìnxī. Zhè yīnggāi shì nín zuìhòu biānxiě de bùfèn, yǐ
-    quèbǎo tā zhǔnquè fǎnyìng wéndàng de nèiróng.
 
@@
 
+    \section{Introduction}
+    \label{sec:intro}
+
+    Target speaker separation (TSS) has attracted much attention in recent years~\cite{speakerBeam, compact_speakerbeam, voicefilter, li20p_interspeech, time_domain_speaker_ex_net, spex, spex+, speakerfilter, speakerfilter_pro}.
+    It is the task which only extracts the speech of the target speaker in the environment with multiple people speaking simultaneously.
+    The general deep neural network based TSS framework could be summarized as an Encoder (including the speech and speaker encoder)-Separator-Decorder architecture, shown as Figure~\ref{fig:enc_sep_doc_arc}.
+
+    The related works, such as VoiceFilter~\cite{voicefilter}, Atss-Net~\cite{li20p_interspeech}, spex++~\cite{time_domain_speaker_ex_net, spex, spex+}, made efforts in different parts of the aforementioned architecture.
+The Atss-Net introduced attention mechanisms in the separator.
+The spex++ adopted the time-domain method and made lots of changes in the speech and speaker encoder.
+All of them contribute a lot to the development of TSS task.
+
+    Despite the great progress made, we are motivated to explore useful and robust training strategies that could be applied to different model architectures.
+For instance, use new feature as one of the inputs of separator.
+
+    Pitch, or fundamental frequency, is an important characteristic of speech and music signals.
+    The task of pitch extraction, or pitch tracking has a long history.
+There are multiple signal processing based methods to extract pitch.
+A time domain signal processing method is proposed in~\cite{yin} to estimate the foundamental frequency.
+    A frequency-domain signal processing method is proposed in~\cite{swipe}.
+
+    Before the usage of DNN methods for extracting pitch, there are some traditional signal processing methods, and although they have the advantage that the algorithms are easy to understand and do not require training data, they have limitations in terms of accuracy especially in complex environments.
+    Hence, many machine learning based algorithms were developed. A supervised machine learning based algorithm in the time domain is proposed in~\cite{crepe}.
+    A self-supervised machine learning based algorithm in the frequency domain is proposed in~\cite{spice}.
+
+    Using pitch information to help speech separation task also attracts a lot of attention in recent years.
+    A pitch extraction module is concatenated with the separation module together to perform the separation task in~\cite{pitch_aware}.
+    A serial model is built and the final loss is designed as a weighted sum of the speech separation loss and pitch loss in~\cite{serial}.
+However the serial model in~\cite{serial} needs to go through the target speaker extraction first and then perform the pitch tracking after the extraction.
+
+    \begin{figure}[!t]
+        \centering
+        \includegraphics[width=0.58\linewidth]{img/encoder_sep_decoder}
+        \caption{The Encoder-Separator-Decoder architecture}
+        \label{fig:enc_sep_doc_arc}
+    \end{figure}
+
+    In our paper, we propose a target speaker pitch extraction module which can directly estimate the target speaker's pitch from a mixture of utterances from multiple speakers.
+    Then we explore the strategies on how to contribute this target speaker's pitch information to the target speaker separation task.
+    We propose a small scale Multi-Block RNNoise (MBRNN) model (details in~\ref{subsec:mbrnn_model}) as our baseline speech separation system.
+    Then we propose two training strategies, namely concatenation training and joint training.
+    We further implement these two strategies on multiple models with different scales and the experiment results show that the joint training of the target pitch extraction model and the target speaker separation model is useful to improve the separation performance.
+    The proposed strategies could make positive impact on the TSS task even though the precision of the target pitch extraction is not high enough.
+    The performance of concatenation with ground-truth pitch information show great potential in utilizing the target speaker's pitch information for the TSS task.
+
+    \section{Model Architecture}
+    \label{sec:architecture}
+
+    In this section, we give a detailed description of our target pitch extraction module and the training strategies of incorporating pitch information in the speech separation model.
+    We have three modules in our framework: 1) the speaker embedding extraction module, which accepts the enrollment utterance and outputs the 128-dimensional speaker embedding the same way as in~\cite{li20p_interspeech}.
+2) the target pitch extraction module, which accepts the magnitude spectrogram of the mixed utterance and the target speaker embedding, then outputs the 1-dimensional target pitch value; 3) the TSS module, which accepts the mixed utterance, the target speaker embedding, the target pitch information, then ouputs the estimated target speaker's voice.
+
+    \subsection{Training strategies with pitch}
+    \label{subsec:two_training_strategy}
+
+    \subsubsection{Concatenation}
+    \label{subsubsec:pitch_cat}
+    The architecture of the TSS model with simply pitch information concatenated is illustrated in Figure~\ref{fig:pitch_concatenate}.
+
+    The extracted target pitch, together with the speaker embedding, are concatenated with the audio feature along the feature axis and then fed into the speech separation model.
+In this concatenation strategy, the speaker embedding extraction module and the target pitch extraction module are all pre-trained well-performed models.
+Thus the parameters of both models are frozen in the speech separation stage.
+
+    \begin{figure}[t]
+        \centering
+        \includegraphics[width=0.8\linewidth]{img/overall_architecture}
+        \caption{TSS model with pitch concatenation.}
+        \label{fig:pitch_concatenate}
+    \end{figure}
+
+    \subsubsection{Joint training}
+    \label{subsubsec:pitch_joint}
+
+    The structure of joint training is as same as in section~\ref{subsubsec:pitch_cat}.
+    The difference is that the target pitch extraction model and the TSS model are optimized jointly.
+The experimental results of this strategy suggest better performance than the concatenation strategy.
+
+    \subsection{Target pitch extraction module}
+    \label{subsec:pitch_model}
+    Our target pitch extraction model is LSTM-based. The structure is shown in Figure~\ref{fig:tp_extraction}.
+    The model takes in the spectrogram of the mixed utterance and the target speaker embedding, and outputs the 1-dimensional pitch information $f_0\in\mathbb{R}^{T\times 1}$ of the target speaker, where $T$ is the number of frames of the mixed utterance.
+    The ground-truth pitch information is extracted using the RAPT algorithm~\cite{Talkin2005ARA} on the pre-mix clean signal, the pitch range is set to $60\sim404$ Hz.
+    We see this target pitch extraction work as a regression problem and adopt L1 loss as the loss function:
+    \begin{equation}
+        L = min|\hat{f}_{0}-f_{0}|
+    \end{equation}
+    where $\hat{f}_{0}$, $f_{0}$ denote the estimated and the ground-truth pitch respectively.
+
+    We employ the precision rate (PR) to evaluate the pitch extraction result~\cite{zhang16d_interspeech}, which is defined as follow:
+    \begin{equation}
+        PR =\frac{N^{0.05}}{N}
+    \end{equation}
+    where ${N^{0.05}}$ denotes the number of frames in which the estimated pitch deviates less than $5\%$ from the ground-truth pitch, and $N$ denotes the total frames of mixed utterance.
+
+    \begin{figure}[t]
+        \centering
+        \includegraphics[width=\linewidth]{img/tp_model}
+        \caption{Model structure of pitch extraction model.}
+        \label{fig:tp_extraction}
+    \end{figure}
+
+    \subsection{MBRNN}
+    \label{subsec:mbrnn_model}
+    Our proposed small scale separation model, named as Multi-Block RNNoise (MBRNN), is modified from the well-known RNNoise~\cite{rnnoise} model in speech enhancement.
+    The architecture of MBRNN model is shown in Figure~\ref{fig:mbrnn_pitch}.
+Each RNNblock in MBRNN includes a fully-connected (FC) layer and a RNNoise-like module (shown in Figure~\ref{fig:rnnBlock}).
+    After the concatenation between speaker embedding and the magnitude spectrogram, the FC layer is used to compress the feature dimension into a fixed smaller scope.
+    The RNNblock is repeated for 4 times to improve the representational capacity.
+    In order to ease the training problem of deep neural network, a cumulative layer normalizaton (cLN)~\cite{conv_tasnet} is adopted between RNNoise blocks.
+
+    We use a Conv1D layer to accelerate the computation of STFT.
+    As the regular time-frequency domain method, only the magnitude spectrogram of the mixed uttenrace $X\in\mathbb{R}^{T\times F}$ is fed into the following network, the phase spectrogram $P\in\mathbb{R}^{T\times F}$ is used to reconstruct the estimated target signal at the end, where $T$ denotes the number of frames and $F$ denotes the spectrogram bin axis.
+    The estimated magnitude spectrogram is the element-wise product between the mixed spectrogram and the estimated mask $M\in\mathbb{R}^{T\times F}$.
+The estimated magnitude spectrogram and the mixed phase spectrogram $P$ are fed into a Conv-Trans1D to perform inverse short-time Fourier transform (iSTFT) to get the estimated target speech.
+    It can be expressed as equation~\ref{eq:est_wav_eq}:
+    \begin{equation}
+        \label{eq:est_wav_eq}
+        \hat{s} = \text{Conv\_iSTFT}\left( \text{ReLU}\left( M\odot X \right), P \right)
+    \end{equation}
+    And we choose scale-invariant source-to-noise ratio (SI-SNR) as our training target~\cite{tasnet}.
+
+    \begin{figure}[t]
+        \centering
+        \includegraphics[width=\linewidth]{img/mbrnn_pitch}
+        \caption{Model architecture of MBRNN model combining with target pitch information, the left side of the figure is the whole architecture of MBRNN with target pitch, the right side of the figure is the detail structure of Mag\_mask Net in the left side, for our experiments, we choose the number of RNN Blocks is 4.}
+        \label{fig:mbrnn_pitch}
+    \end{figure}
+
+    \begin{figure}[t]
+        \centering
+        \includegraphics[width=0.7\linewidth]{img/rnnBlock.png}
+        \caption{Detailed structure of RNN Block in MBRNN model.}
+        \label{fig:rnnBlock}
+    \end{figure}
+
+    \section{Experiments}
+    \label{sec:exp_result}
+
+    \subsection{Dataset description}
+    \label{subsec:dataset}
+
+    Our experiments are conducted on the LibriSpeech dataset, and we use the same training and testing tuple as same as Google used in VoiceFilter~\cite{voicefilter}.
+The mixed utterances are all truncated to 5 seconds in the training stage.
+We mix the utterances to 0dB in SNR.
+
+    \subsection{Target pitch training}
+    \label{subsec:target_pitch_training}
+
+    The hidden units of LSTM in the target pitch extraction is set to 300.
+The window length and hop size are 25ms and 10ms as same as the speech separation model used.
+And we perform a 512-point STFT on the mixed utterance.
+To evaluate the pitch extraction ability of our model, we also trained a clean pitch extractor on single speaker clean data.
+The PR result is shown in Table~\ref{tab:pitch result}.
+
+    \begin{table}[htbp]
+        \centering
+        \begin{tabular}{c|c}
+            \toprule
+            Type                                          & PR($\%$) \\
+            \midrule
+            Single speaker pitch extraction on clean data & 93.06    \\
+            \midrule
+            Target pitch extractor on mixture data        & 70.27    \\
+            \bottomrule
+        \end{tabular}
+        \caption{PR results of different type of pitch extraction models.}
+        \label{tab:pitch result}
+    \end{table}
+
+    A target pitch extraction examples selected from the test set is shown in Figure~\ref{fig:pitch_1}.
+    \begin{figure}[t]
+        \stackunder[5pt]{\includegraphics[width=\linewidth]{img/pitch.eps}}{(a)}
+        \stackunder[5pt]{\includegraphics[width=\linewidth]{img/spec_mix.eps}}{(b)}
+        \stackunder[5pt]{\includegraphics[width=\linewidth]{img/spec_target.eps}}{(c)}
+
+        \caption{Target pitch extraction result of 2506-11267-0005 item in the test set.
+(a) Estimated pitch compared with the ground-truth pitch; (b) and (c) Estimated and ground-truth pitch respectively represented on the magnitude spectrogram, only the low frequency part is showed.
+}
+        \label{fig:pitch_1}
+    \end{figure}
+
+    \begin{table*}[!htbp]
+        \centering
+        \begin{tabular}{l|c|c|c|c}
+            \toprule
+            & \multicolumn{4}{c}{Mean SDR} \\
+            Model (strategy)                             & \#PARAM TSS(TPE) & Before & After         & Improvement   \\
+            \midrule
+            MBRNN (Baseline)                             & 0.60M            & 1.26   & 6.09          & 4.83          \\
+            MBRNN Pitch (Concatenation)                  & 0.60M(1.46M)     & 1.26   & 6.28          & 5.02          \\
+            MBRNN Pitch (Joint train)                    & 0.60M(1.46M)     & 1.26   & \textbf{7.11} & \textbf{5.85} \\
+            MBRNN Pitch (Ground truth pitch)             & 0.60M            & 1.26   & 9.80          & 8.54          \\
+            \midrule
+            Our implementation of VoiceFilter (Baseline) & 15.52M           & 1.26   & 9.02          & 7.76          \\
+            Our implementation of VoiceFilter Pitch (Joint train) & 15.53M(1.46M) & 1.26 & \textbf{9.20}
+            & \textbf{7.94}
+            \\
+            \midrule
+            VoiceFilter~\cite{voicefilter} (Baseline)    & 9.45M            & 1.26   & 9.04          & 7.78          \\
+            VoiceFilter~\cite{voicefilter} Pitch (Joint train) & 9.46M(1.46M) & 1.26 & \textbf{9.60}
+            & \textbf{8.34}
+            \\
+            \bottomrule
+        \end{tabular}
+        \caption{Results comparison between different training strategies and the baseline with MBRNN and VoiceFilter model.
+``Before" means the SDR value of the mixed utterance, ``After" means the SDR value of the estimated speech.}
+        \label{tab:mbrnn_comparison}
+    \end{table*}
+
+    \subsection{Implementation details}
+    \label{subsec:implement}
+
+    Our experiments are done using PyTorch~\cite{NEURIPS2019_bdbca288}.
+    In Table~\ref{tab:mbrnn_comparison}, TSS and target pitch extraction (TPE) mean the number of model parameters of speech separation model and target pitch extraction model respectively.
+    MBRNN (Baseline) means the baseline MBRNN model which does not use target pitch information.
+MBRNN Pitch (Concatenation) and MBRNN Pitch (Joint train) mean the MBRNN model uses target pitch information with the training strategy in Section~\ref{subsubsec:pitch_cat} and Section~\ref{subsubsec:pitch_joint} respectively.
+
+    We also validate our proposed methods on the well known VoiceFilter baseline model which has larger scale compared to our MBRNN model.
+For the VoiceFilter model, we use MSE loss instead of SI-SNR loss for all experiments for keeping the same setup as the original one.
+However for the faster training time, we change the channels to 16 in CNNs for those which are originally 64 and 8 in VoiceFilter.
+The re-implementation in~\cite{li20p_interspeech} of VoiceFilter is 9.04, the re-implementation of VoiceFilter here is 9.02.
+    Both separation models and target pitch extraction model, we did 512-point STFT on the utterance, the window length is 25ms and the hop length is 10ms.
+The frequency dimension of the spectrogram is 257 and the embedding dimension is 128.
+
+    In the target pitch extraction module, the first fully connected layer (FC 1) maps the vector from frequency dimension (257) into embedding dimension (128).
+Then concatenate with the embedding, so the input dimension into LSTM is $2\times \text{embedding\_dim}$.
+In LSTM, the hidden dimension is 300, number of recurrent layers is 2, set dropout as 0.3.
+For FC 2, it maps the dimension from 300 to 128, a ReLU activation is added after FC 2.
+FC 3 maps the dimension from 128 to 1 and set ReLU activation after FC 3.
+
+    In RNN Block in MBRNN model, FC 1 maps from $\text{embedding\_dim}$ to $\text{embedding\_dim} - 1$.
+Before FC 2, concatenate the three inputs.
+FC 2 maps from $\text{hidden\_dim}\times\text{amp} + \text{embedding\_dim}$ to $\text{rnn\_units}\times\text{amp}$, $\text{amp}$ and $\text{rnn\_units}$ are set to 1 and 38 respectively in our experiments.
+FC 3 maps to 24.
+For LSTM 1 - 3, the hidden sizes are 24, 48, 96 respectively.
+FC 4 maps dimension to 64.
+The output of each RNN Block is the sum of the output from FC 4 and the output feature from the last layer before RNN Block.
+
+    All the experiments use Adam optimizer~\cite{kingma2017adam} and $10^{-4}$ as initial learning rate.
+    For the experiments which choose MBRNN as the baseline, their batch size are 128, and for VoiceFilter, their batch size are 64.
+
+    \subsection{Results discussion}
+    \label{subsec:results_discussion}
+
+    From Table~\ref{tab:mbrnn_comparison}, due to the small model size of MBRNN, the baseline of MBRNN is a little bit weak.
+But from the results of both MBRNN and VoiceFilter we can see that target pitch information can help TSS model no matter in small model and large model.
+    For the concatenation training strategy in MBRNN, it can improve 5.02 dB compared to 4.83 dB in the baseline, and the joint training strategy can improve 5.85 dB.
+So joint training strategy is 0.83 dB higher than the concatenation strategy.
+    To validate the idea that the target pitch information is indeed useful for TSS model, we use the ground truth target pitch and found out it can help MBRNN reach 8.54dB improvement which is very significant, 2.69dB higher compared to the joint training strategy.
+    We can see that a high PR target pitch extraction can really help the TSS model, even without high precision target pitch extraction, by using the joint training strategy, it can still help the TSS model improve the performance.
+
+    Moreover, from the experiments done on the VoiceFilter baseline, we can show that the joint training strategy on TSS model and pre-trained target pitch extraction model is a robust strategy to help TSS model improve the performance.
+    And our experiments showed that even though the precision of target pitch extraction is not very high, the joint training strategy is better than simply concatenating pitch.
+
+    For the future works, we will continue to work on using target pitch on the time-domain model.
+
+    \section{Conclusions}
+    \label{sec:conclusions}
+    In this paper, we propose the idea that using target speaker's pitch as an auxiliary feature to improve the performance of target speaker separation.
+A target pitch extraction model is built and the target pitch information is incorporated with the TSS models in both simply concatenation and joint training strategies.
+We found that the target pitch information could improve the separation performance even though the pitch precision is not high enough yet.
+While the performance of concatenation with ground-truth pitch information show the great potency of this approach.
+The joint training approach yields better performance than simple concatenation.
+We also explore if joint training would bring improvement to the target pitch extraction, the result shows no obvious help.
+In the future work, we will continue to improve the precision of target pitch extraction and do more experiments on large scale models to validate the proposed methods.
+
+    \bibliographystyle{IEEEbib}
+    \bibliography{Odyssey2022_BibEntries}
+
 \end{document}

### 2022-04-23 Paper.tex
Refactor the latex code

--- 2022-04-21 Paper.tex
@@
+%! Author = jincheng
+
 % Options for packages loaded elsewhere
@@
     150 - 200
-    字。摘要是对问题或研究目的的简要说明。说明所使用的理论工作或实验计划，总结研究的主要发现，并指出主要结论。适用时应包括适当的安全信息。这应该是您最后编写的部分，以确保它准确反映文档的内容。
-
-    150 - 200 Zì. Zhāiyào shi duì wèntí huò yánjiū mùdì de jiǎnyào shuōmíng.
-    Shuōmíng suǒ shǐyòng de lǐlùn gōngzuò huò shíyàn jìhuà, zǒngjié yánjiū
-    de zhǔyào fāxiàn, bìng zhǐchū zhǔyào jiélùn. Shìyòng shí yīng bāokuò
-    shìdàng de ānquán xìnxī. Zhè yīnggāi shì nín zuìhòu biānxiě de bùfèn, yǐ
-    quèbǎo tā zhǔnquè fǎnyìng wéndàng de nèiróng.
 
     \section{ACKNOWLEDGEMENTS}\label{acknowledgements}
+    \newpage
 
     \tableofcontents
+    \newpage
+
+    \input{introduction.tex}
+
+    \input{model_architecture.tex}
+
+    \input{experiments.tex}
+
+    \input{conclusions.tex}
+
+    \bibliographystyle{IEEEbib}
+    \bibliography{Odyssey2022_BibEntries}
 

### 2022-04-23 conclusions.tex
Refactor the latex code

%! Author = jincheng
%! Date = 2022/4/23

\section{Conclusions}
\label{sec:conclusions}
In this paper, we propose the idea that using target speaker's pitch as an auxiliary feature to improve the performance of target speaker separation. A target pitch extraction model is built and the target pitch information is incorporated with the TSS models in both simply concatenation and joint training strategies. We found that the target pitch information could improve the separation performance even though the pitch precision is not high enough yet. While the performance of concatenation with ground-truth pitch information show the great potency of this approach. The joint training approach yields better performance than simple concatenation. We also explore if joint training would bring improvement to the target pitch extraction, the result shows no obvious help. In the future work, we will continue to improve the precision of target pitch extraction and do more experiments on large scale models to validate the proposed methods.

### 2022-04-23 experiments.tex
Refactor the latex code

%! Author = jincheng
%! Date = 2022/4/23

\section{Experiments}
\label{sec:exp_result}

\subsection{Dataset description}
\label{subsec:dataset}

Our experiments are conducted on the LibriSpeech dataset, and we use the same training and testing tuple as same as Google used in VoiceFilter~\cite{voicefilter}. The mixed utterances are all truncated to 5 seconds in the training stage. We mix the utterances to 0dB in SNR.

\subsection{Target pitch training}
\label{subsec:target_pitch_training}

The hidden units of LSTM in the target pitch extraction is set to 300. The window length and hop size are 25ms and 10ms as same as the speech separation model used. And we perform a 512-point STFT on the mixed utterance. To evaluate the pitch extraction ability of our model, we also trained a clean pitch extractor on single speaker clean data. The PR result is shown in Table~\ref{tab:pitch result}.

\begin{table}[htbp]
    \centering
    \begin{tabular}{c|c}
        \toprule
        Type                                          & PR($\%$) \\
        \midrule
        Single speaker pitch extraction on clean data & 93.06    \\
        \midrule
        Target pitch extractor on mixture data        & 70.27    \\
        \bottomrule
    \end{tabular}
    \caption{PR results of different type of pitch extraction models.}
    \label{tab:pitch result}
\end{table}

A target pitch extraction examples selected from the test set is shown in Figure~\ref{fig:pitch_1}.
\begin{figure}[t]
    \stackunder[5pt]{\includegraphics[width=\linewidth]{img/pitch.eps}}{(a)}
    \stackunder[5pt]{\includegraphics[width=\linewidth]{img/spec_mix.eps}}{(b)}
    \stackunder[5pt]{\includegraphics[width=\linewidth]{img/spec_target.eps}}{(c)}

    \caption{Target pitch extraction result of 2506-11267-0005 item in the test set. (a) Estimated pitch compared with the ground-truth pitch; (b) and (c) Estimated and ground-truth pitch respectively represented on the magnitude spectrogram, only the low frequency part is showed. }
    \label{fig:pitch_1}
\end{figure}

\begin{table*}[!htbp]
    \centering
    \begin{tabular}{l|c|c|c|c}
        \toprule
        & \multicolumn{4}{c}{Mean SDR} \\
        Model (strategy)                             & \#PARAM TSS(TPE) & Before & After         & Improvement   \\
        \midrule
        MBRNN (Baseline)                             & 0.60M            & 1.26   & 6.09          & 4.83          \\
        MBRNN Pitch (Concatenation)                  & 0.60M(1.46M)     & 1.26   & 6.28          & 5.02          \\
        MBRNN Pitch (Joint train)                    & 0.60M(1.46M)     & 1.26   & \textbf{7.11} & \textbf{5.85} \\
        MBRNN Pitch (Ground truth pitch)             & 0.60M            & 1.26   & 9.80          & 8.54          \\
        \midrule
        Our implementation of VoiceFilter (Baseline) & 15.52M           & 1.26   & 9.02          & 7.76          \\
        Our implementation of VoiceFilter Pitch (Joint train) & 15.53M(1.46M) & 1.26 & \textbf{9.20}
        & \textbf{7.94}
        \\
        \midrule
        VoiceFilter~\cite{voicefilter} (Baseline)    & 9.45M            & 1.26   & 9.04          & 7.78          \\
        VoiceFilter~\cite{voicefilter} Pitch (Joint train) & 9.46M(1.46M) & 1.26 & \textbf{9.60}
        & \textbf{8.34}
        \\
        \bottomrule
    \end{tabular}
    \caption{Results comparison between different training strategies and the baseline with MBRNN and VoiceFilter model. ``Before" means the SDR value of the mixed utterance, ``After" means the SDR value of the estimated speech.}
    \label{tab:mbrnn_comparison}
\end{table*}

\subsection{Implementation details}
\label{subsec:implement}

Our experiments are done using PyTorch~\cite{NEURIPS2019_bdbca288}.
In Table~\ref{tab:mbrnn_comparison}, TSS and target pitch extraction (TPE) mean the number of model parameters of speech separation model and target pitch extraction model respectively.
MBRNN (Baseline) means the baseline MBRNN model which does not use target pitch information. MBRNN Pitch (Concatenation) and MBRNN Pitch (Joint train) mean the MBRNN model uses target pitch information with the training strategy in Section~\ref{subsubsec:pitch_cat} and Section~\ref{subsubsec:pitch_joint} respectively.

We also validate our proposed methods on the well known VoiceFilter baseline model which has larger scale compared to our MBRNN model. For the VoiceFilter model, we use MSE loss instead of SI-SNR loss for all experiments for keeping the same setup as the original one. However for the faster training time, we change the channels to 16 in CNNs for those which are originally 64 and 8 in VoiceFilter. The re-implementation in~\cite{li20p_interspeech} of VoiceFilter is 9.04, the re-implementation of VoiceFilter here is 9.02.
Both separation models and target pitch extraction model, we did 512-point STFT on the utterance, the window length is 25ms and the hop length is 10ms. The frequency dimension of the spectrogram is 257 and the embedding dimension is 128.

In the target pitch extraction module, the first fully connected layer (FC 1) maps the vector from frequency dimension (257) into embedding dimension (128). Then concatenate with the embedding, so the input dimension into LSTM is $2\times \text{embedding\_dim}$. In LSTM, the hidden dimension is 300, number of recurrent layers is 2, set dropout as 0.3. For FC 2, it maps the dimension from 300 to 128, a ReLU activation is added after FC 2. FC 3 maps the dimension from 128 to 1 and set ReLU activation after FC 3.

In RNN Block in MBRNN model, FC 1 maps from $\text{embedding\_dim}$ to $\text{embedding\_dim} - 1$. Before FC 2, concatenate the three inputs. FC 2 maps from $\text{hidden\_dim}\times\text{amp} + \text{embedding\_dim}$ to $\text{rnn\_units}\times\text{amp}$, $\text{amp}$ and $\text{rnn\_units}$ are set to 1 and 38 respectively in our experiments. FC 3 maps to 24. For LSTM 1 - 3, the hidden sizes are 24, 48, 96 respectively. FC 4 maps dimension to 64. The output of each RNN Block is the sum of the output from FC 4 and the output feature from the last layer before RNN Block.

All the experiments use Adam optimizer~\cite{kingma2017adam} and $10^{-4}$ as initial learning rate.
For the experiments which choose MBRNN as the baseline, their batch size are 128, and for VoiceFilter, their batch size are 64.

\subsection{Results discussion}
\label{subsec:results_discussion}

From Table~\ref{tab:mbrnn_comparison}, due to the small model size of MBRNN, the baseline of MBRNN is a little bit weak. But from the results of both MBRNN and VoiceFilter we can see that target pitch information can help TSS model no matter in small model and large model.
For the concatenation training strategy in MBRNN, it can improve 5.02 dB compared to 4.83 dB in the baseline, and the joint training strategy can improve 5.85 dB. So joint training strategy is 0.83 dB higher than the concatenation strategy.
To validate the idea that the target pitch information is indeed useful for TSS model, we use the ground truth target pitch and found out it can help MBRNN reach 8.54dB improvement which is very significant, 2.69dB higher compared to the joint training strategy.
We can see that a high PR target pitch extraction can really help the TSS model, even without high precision target pitch extraction, by using the joint training strategy, it can still help the TSS model improve the performance.

Moreover, from the experiments done on the VoiceFilter baseline, we can show that the joint training strategy on TSS model and pre-trained target pitch extraction model is a robust strategy to help TSS model improve the performance.
And our experiments showed that even though the precision of target pitch extraction is not very high, the joint training strategy is better than simply concatenating pitch.

For the future works, we will continue to work on using target pitch on the time-domain model.

### 2022-04-23 introduction.tex
Refactor the latex code

%! Author = jincheng
%! Date = 2022/4/23

\section{Introduction}
\label{sec:intro}

Target speaker separation (TSS) has attracted much attention in recent years~\cite{speakerBeam, compact_speakerbeam, voicefilter, li20p_interspeech, time_domain_speaker_ex_net, spex, spex+, speakerfilter, speakerfilter_pro}.
It is the task which only extracts the speech of the target speaker in the environment with multiple people speaking simultaneously.
The general deep neural network based TSS framework could be summarized as an Encoder (including the speech and speaker encoder)-Separator-Decorder architecture, shown as Figure~\ref{fig:enc_sep_doc_arc}.

The related works, such as VoiceFilter~\cite{voicefilter}, Atss-Net~\cite{li20p_interspeech}, spex++~\cite{time_domain_speaker_ex_net, spex, spex+}, made efforts in different parts of the aforementioned architecture. The Atss-Net introduced attention mechanisms in the separator. The spex++ adopted the time-domain method and made lots of changes in the speech and speaker encoder. All of them contribute a lot to the development of TSS task.

Despite the great progress made, we are motivated to explore useful and robust training strategies that could be applied to different model architectures. For instance, use new feature as one of the inputs of separator.

Pitch, or fundamental frequency, is an important characteristic of speech and music signals.
The task of pitch extraction, or pitch tracking has a long history. There are multiple signal processing based methods to extract pitch. A time domain signal processing method is proposed in~\cite{yin} to estimate the foundamental frequency.
A frequency-domain signal processing method is proposed in~\cite{swipe}.

Before the usage of DNN methods for extracting pitch, there are some traditional signal processing methods, and although they have the advantage that the algorithms are easy to understand and do not require training data, they have limitations in terms of accuracy especially in complex environments.
Hence, many machine learning based algorithms were developed. A supervised machine learning based algorithm in the time domain is proposed in~\cite{crepe}.
A self-supervised machine learning based algorithm in the frequency domain is proposed in~\cite{spice}.

Using pitch information to help speech separation task also attracts a lot of attention in recent years.
A pitch extraction module is concatenated with the separation module together to perform the separation task in~\cite{pitch_aware}.
A serial model is built and the final loss is designed as a weighted sum of the speech separation loss and pitch loss in~\cite{serial}. However the serial model in~\cite{serial} needs to go through the target speaker extraction first and then perform the pitch tracking after the extraction.

\begin{figure}[!t]
    \centering
    \includegraphics[width=0.58\linewidth]{img/encoder_sep_decoder}
    \caption{The Encoder-Separator-Decoder architecture}
    \label{fig:enc_sep_doc_arc}
\end{figure}

In our paper, we propose a target speaker pitch extraction module which can directly estimate the target speaker's pitch from a mixture of utterances from multiple speakers.
Then we explore the strategies on how to contribute this target speaker's pitch information to the target speaker separation task.
We propose a small scale Multi-Block RNNoise (MBRNN) model (details in~\ref{subsec:mbrnn_model}) as our baseline speech separation system.
Then we propose two training strategies, namely concatenation training and joint training.
We further implement these two strategies on multiple models with different scales and the experiment results show that the joint training of the target pitch extraction model and the target speaker separation model is useful to improve the separation performance.
The proposed strategies could make positive impact on the TSS task even though the precision of the target pitch extraction is not high enough.
The performance of concatenation with ground-truth pitch information show great potential in utilizing the target speaker's pitch information for the TSS task.

### 2022-04-23 model_architecture.tex
Refactor the latex code

%! Author = jincheng
%! Date = 2022/4/23

\section{Model Architecture}
\label{sec:architecture}

In this section, we give a detailed description of our target pitch extraction module and the training strategies of incorporating pitch information in the speech separation model.
We have three modules in our framework: 1) the speaker embedding extraction module, which accepts the enrollment utterance and outputs the 128-dimensional speaker embedding the same way as in~\cite{li20p_interspeech}. 2) the target pitch extraction module, which accepts the magnitude spectrogram of the mixed utterance and the target speaker embedding, then outputs the 1-dimensional target pitch value; 3) the TSS module, which accepts the mixed utterance, the target speaker embedding, the target pitch information, then ouputs the estimated target speaker's voice.

\subsection{Training strategies with pitch}
\label{subsec:two_training_strategy}

\subsubsection{Concatenation}
\label{subsubsec:pitch_cat}
The architecture of the TSS model with simply pitch information concatenated is illustrated in Figure~\ref{fig:pitch_concatenate}.

The extracted target pitch, together with the speaker embedding, are concatenated with the audio feature along the feature axis and then fed into the speech separation model. In this concatenation strategy, the speaker embedding extraction module and the target pitch extraction module are all pre-trained well-performed models. Thus the parameters of both models are frozen in the speech separation stage.

\begin{figure}[t]
    \centering
    \includegraphics[width=0.8\linewidth]{img/overall_architecture}
    \caption{TSS model with pitch concatenation.}
    \label{fig:pitch_concatenate}
\end{figure}

\subsubsection{Joint training}
\label{subsubsec:pitch_joint}

The structure of joint training is as same as in section~\ref{subsubsec:pitch_cat}.
The difference is that the target pitch extraction model and the TSS model are optimized jointly. The experimental results of this strategy suggest better performance than the concatenation strategy.

\subsection{Target pitch extraction module}
\label{subsec:pitch_model}
Our target pitch extraction model is LSTM-based. The structure is shown in Figure~\ref{fig:tp_extraction}.
The model takes in the spectrogram of the mixed utterance and the target speaker embedding, and outputs the 1-dimensional pitch information $f_0\in\mathbb{R}^{T\times 1}$ of the target speaker, where $T$ is the number of frames of the mixed utterance.
The ground-truth pitch information is extracted using the RAPT algorithm~\cite{Talkin2005ARA} on the pre-mix clean signal, the pitch range is set to $60\sim404$ Hz.
We see this target pitch extraction work as a regression problem and adopt L1 loss as the loss function:
\begin{equation}
    L = min|\hat{f}_{0}-f_{0}|
\end{equation}
where $\hat{f}_{0}$, $f_{0}$ denote the estimated and the ground-truth pitch respectively.

We employ the precision rate (PR) to evaluate the pitch extraction result~\cite{zhang16d_interspeech}, which is defined as follow:
\begin{equation}
    PR =\frac{N^{0.05}}{N}
\end{equation}
where ${N^{0.05}}$ denotes the number of frames in which the estimated pitch deviates less than $5\%$ from the ground-truth pitch, and $N$ denotes the total frames of mixed utterance.

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{img/tp_model}
    \caption{Model structure of pitch extraction model.}
    \label{fig:tp_extraction}
\end{figure}

\subsection{MBRNN}
\label{subsec:mbrnn_model}
Our proposed small scale separation model, named as Multi-Block RNNoise (MBRNN), is modified from the well-known RNNoise~\cite{rnnoise} model in speech enhancement.
The architecture of MBRNN model is shown in Figure~\ref{fig:mbrnn_pitch}. Each RNNblock in MBRNN includes a fully-connected (FC) layer and a RNNoise-like module (shown in Figure~\ref{fig:rnnBlock}).
After the concatenation between speaker embedding and the magnitude spectrogram, the FC layer is used to compress the feature dimension into a fixed smaller scope.
The RNNblock is repeated for 4 times to improve the representational capacity.
In order to ease the training problem of deep neural network, a cumulative layer normalizaton (cLN)~\cite{conv_tasnet} is adopted between RNNoise blocks.

We use a Conv1D layer to accelerate the computation of STFT.
As the regular time-frequency domain method, only the magnitude spectrogram of the mixed uttenrace $X\in\mathbb{R}^{T\times F}$ is fed into the following network, the phase spectrogram $P\in\mathbb{R}^{T\times F}$ is used to reconstruct the estimated target signal at the end, where $T$ denotes the number of frames and $F$ denotes the spectrogram bin axis.
The estimated magnitude spectrogram is the element-wise product between the mixed spectrogram and the estimated mask $M\in\mathbb{R}^{T\times F}$. The estimated magnitude spectrogram and the mixed phase spectrogram $P$ are fed into a Conv-Trans1D to perform inverse short-time Fourier transform (iSTFT) to get the estimated target speech.
It can be expressed as equation~\ref{eq:est_wav_eq}:
\begin{equation}
    \label{eq:est_wav_eq}
    \hat{s} = \text{Conv\_iSTFT}\left( \text{ReLU}\left( M\odot X \right), P \right)
\end{equation}
And we choose scale-invariant source-to-noise ratio (SI-SNR) as our training target~\cite{tasnet}.

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{img/mbrnn_pitch}
    \caption{Model architecture of MBRNN model combining with target pitch information, the left side of the figure is the whole architecture of MBRNN with target pitch, the right side of the figure is the detail structure of Mag\_mask Net in the left side, for our experiments, we choose the number of RNN Blocks is 4.}
    \label{fig:mbrnn_pitch}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=0.7\linewidth]{img/rnnBlock.png}
    \caption{Detailed structure of RNN Block in MBRNN model.}
    \label{fig:rnnBlock}
\end{figure}

### 2022-04-23 experiments.tex
Reformat the paper

@@
 A target pitch extraction examples selected from the test set is shown in Figure~\ref{fig:pitch_1}.
-\begin{figure}[t]
-    \stackunder[5pt]{\includegraphics[width=\linewidth]{img/pitch.eps}}{(a)}
-    \stackunder[5pt]{\includegraphics[width=\linewidth]{img/spec_mix.eps}}{(b)}
-    \stackunder[5pt]{\includegraphics[width=\linewidth]{img/spec_target.eps}}{(c)}
+\begin{figure}[!htbp]
+    \centering
+    \stackunder[5pt]{\includegraphics[width=0.45\linewidth]{img/pitch.eps}}{(a)}
+    \stackunder[5pt]{\includegraphics[width=0.45\linewidth]{img/spec_mix.eps}}{(b)}
+    \stackunder[5pt]{\includegraphics[width=0.45\linewidth]{img/spec_target.eps}}{(c)}
 

### 2022-04-23 Paper.tex
Rename the bib file
Add title
Reformat the paper
Add English and Chinese abstracts

@@
 \IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
+%\makesavenoteenv{longtable}
 \usepackage{graphicx}
@@
 \setcounter{secnumdepth}{-\maxdimen} % remove section numbering
-\ifLuaTeX
-\usepackage{selnolig}  % disable illegal ligatures
-\fi
+
 \usepackage{stackengine}
+\usepackage{setspace}
+\usepackage{geometry}
+\usepackage{CJKutf8}
+\geometry{left=2.5cm,right=2.5cm}
 
@@
 
-    THESIS TITLE THAT EXTENDS OVER ONE LINE GOES IN INVERTED PYRAMID FORM
+    A STUDY ON THE DEEP LEARNING BASED TARGET SPEAKER SPEECH SEPARATION ALGORITHMS
 
@@
 
-    \emph{150 -- 200 words}. \emph{An abstract is a brief statement of the
-    problem or the purpose of the research. It should indicate the
-    theoretical work or experimental plan used, summarize principal findings
-    of the research, and point out major conclusions. Appropriate safety
-    information should be included when applicable. This should be the
-    section you write last to be sure that it accurately reflects the
-    content of the document.}
+    Despite the great progress achieved in the target speaker separation (TSS) task, we are still trying to find other robust ways for performance improvement which are independent of the model architecture and the training loss.
+    Pitch extraction plays an important role in many applications such as speech enhancement and speech separation.
+    It is also a challenging task when there are multiple speakers in the same utterance.
+    In this paper, we explore if the target speaker pitch extraction is possible and how the extracted target pitch could help to improve the TSS performance.
+    A target pitch extraction model is built and incorporated into different TSS models using two different strategies, namely concatenation and joint training.
+    The experimental results on the LibriSpeech dataset show that both training strategies could bring significant improvements to the TSS task, even the precision of the target pitch extraction module is not high enough.
 
@@
 
-    150 - 200
+    \begin{CJK}{UTF8}{gbsn}
+        尽管在目标说话人分离 (TSS) 任务中取得了巨大进展，但我们仍在尝试寻找其他独立于模型架构和训练损失的稳健方法来提高性能。
+        音高提取在语音增强和语音分离等许多应用中发挥着重要作用。
+        当同一话语中有多个说话者时，这也是一项具有挑战性的任务。
+        在本文中，我们探讨了目标说话人音高提取是否可行，以及提取的目标音高如何有助于提高 TSS 性能。
+        使用两种不同的策略，即连接和联合训练，构建目标基音提取模型并将其合并到不同的 TSS 模型中。
+        在 LibriSpeech 数据集上的实验结果表明，这两种训练策略都可以为 TSS 任务带来显着的改进，即使目标音高提取模块的精度不够高。
+    \end{CJK}
 
@@
 
+    \begin{spacing}{1.5}
         \input{introduction.tex}
@@
         \bibliographystyle{IEEEbib}
-    \bibliography{Odyssey2022_BibEntries}
+        \bibliography{reference}
+    \end{spacing}
 

### 2022-04-23 Paper.tex
Add reference section into table of contents
Refactor abstract part

--- 2022-04-23 Paper.tex
@@
 
-    \textbf{ABSTRACT} \emph{(in English)}
-
-    \emph{150 -- 200 words}. \emph{An abstract is a brief statement of the
-    problem or the purpose of the research. It should indicate the
-    theoretical work or experimental plan used, summarize principal findings
-    of the research, and point out major conclusions. Appropriate safety
-    information should be included when applicable. This should be the
-    section you write last to be sure that it accurately reflects the
-    content of the document.}
-
-    \textbf{ABSTRACT} \emph{(in Chinese)}
-
-    150 - 200
+    \input{abstract.tex}
 
@@
         \bibliographystyle{IEEEbib}
-    \bibliography{Odyssey2022_BibEntries}
+        \bibliography{reference}
+        \addcontentsline{toc}{section}{References}
+    \end{spacing}
 

### 2022-04-23 abstract.tex
Refactor abstract part

%! Author = jincheng
%! Date = 2022/4/23

\textbf{ABSTRACT} \emph{(in English)}

Despite the great progress achieved in the target speaker separation (TSS) task, we are still trying to find other robust ways for performance improvement which are independent of the model architecture and the training loss.
Pitch extraction plays an important role in many applications such as speech enhancement and speech separation.
It is also a challenging task when there are multiple speakers in the same utterance.
In this paper, we explore if the target speaker pitch extraction is possible and how the extracted target pitch could help to improve the TSS performance.
A target pitch extraction model is built and incorporated into different TSS models using two different strategies, namely concatenation and joint training.
The experimental results on the LibriSpeech dataset show that both training strategies could bring significant improvements to the TSS task, even the precision of the target pitch extraction module is not high enough.

\textbf{ABSTRACT} \emph{(in Chinese)}

\begin{CJK}{UTF8}{gbsn}
    尽管在目标说话人分离 (TSS) 任务中取得了巨大进展，但我们仍在尝试寻找其他独立于模型架构和训练损失的稳健方法来提高性能。
    音高提取在语音增强和语音分离等许多应用中发挥着重要作用。
    当同一话语中有多个说话者时，这也是一项具有挑战性的任务。
    在本文中，我们探讨了目标说话人音高提取是否可行，以及提取的目标音高如何有助于提高 TSS 性能。
    使用两种不同的策略，即连接和联合训练，构建目标基音提取模型并将其合并到不同的 TSS 模型中。
    在 LibriSpeech 数据集上的实验结果表明，这两种训练策略都可以为 TSS 任务带来显着的改进，即使目标音高提取模块的精度不够高。
\end{CJK}

### 2022-04-23 acknowledgements.tex
Add acknowledgements part

%! Author = jincheng
%! Date = 2022/4/23

\section{ACKNOWLEDGEMENTS}\label{sec:acknowledgements}
The first I really want to thank is Prof. Ming Li. I applied to joint Prof. Ming Li's Lab during the summer of my freshman year.
Later on, under the guidance and resources provided by the professor, I started my research in the field of speech analysis technology and speech separation.

### 2022-04-23 acknowledgements.tex
Update the acknowledgements part

@@
 \section{ACKNOWLEDGEMENTS}\label{sec:acknowledgements}
-The first I really want to thank is Prof. Ming Li. I applied to joint Prof. Ming Li's Lab during the summer of my freshman year.
-Later on, under the guidance and resources provided by the professor, I started my research in the field of speech analysis technology and speech separation.
+First and foremost, I would like to thank my research mentor Professor Ming Li who provided huge help to me in the past three years.
+I first met the professor was in the class of CS 101.
+Later on I applied to join Prof. Ming Li's Speech and Multimodal Intelligent Information Processing (SMIIP) Lab during the summer of my freshman year.
+From that time, under the guidance and resources provided by the professor, I started my research in the field of speech analysis technology and speech separation.

### 2022-04-24 acknowledgements.tex
Update acknowledgements part

@@
 First and foremost, I would like to thank my research mentor Professor Ming Li who provided huge help to me in the past three years.
-I first met the professor was in the class of CS 101.
+I first met the professor was in the class of CS 101 Introduction to Computer Science.
 Later on I applied to join Prof. Ming Li's Speech and Multimodal Intelligent Information Processing (SMIIP) Lab during the summer of my freshman year.
 From that time, under the guidance and resources provided by the professor, I started my research in the field of speech analysis technology and speech separation.
+Without the professor's invaluable guidance, my research in the field of speech analysis technology and this signature work cannot happen.
+
+Second, I want to thank my senior schoolfellows Yuanyuan Bao, Yanze Xu, Bang Zeng, Zhan Jin and all the other members in the same lab.
+They provided a lot of help on my path of doing research in target speaker separation (TSS) field.
+It is their help that I can move forward smoother and I learned a lot of skills from them.
+
+Third, I want to thank Summer Research Scholar (SRS) program provided by Duke Kunshan University.
+This program provided research fund during the summer of my junior year.
+
+Last but not least, I want to thank all the members in my family. They have supported me for all my life.

### 2022-04-24 background.tex
Update background what is TSS task

%! Author = jincheng
%! Date = 2022/4/24

\section{Background}\label{sec:background}

In this section, we give a detailed background about what is target speaker separation (TSS) task, what kinds of metrics can be used to define the performance, what kinds of techniques existed can be used to do TSS task.

\subsection{What is TSS task}\label{subsec:what-is-tss-task}

Assume there are $N$ speakers talking simultaneously, they are called $s_1, s_2, \dots s_N$. The speech utterance for each speaker is $U_i$ while $i\in\left[ 1, N \right]$. Assume the noise is $e$.
So the mixed utterance $U$ is as equation~\ref{eq:mixed}.
\begin{equation}
    U = \sum\limits_{i=1}^N U_i + e\label{eq:mixed}
\end{equation}
For the mission of Target Speaker Separation (TSS) Task. Assume we only need to extract the voice of speaker $s_n$ and we have the reference utterance from $s_n$, denoted as $R_n$.
The task is given $U = \sum\limits_{i=1}^N U_i + e$ and $R_n$, we need to get $U_n$.

### 2022-04-24 background.tex
Update metrics SISNR
Update SDR metric
Update background formula

@@
 
-Assume there are $N$ speakers talking simultaneously, they are called $s_1, s_2, \dots s_N$. The speech utterance for each speaker is $U_i$ while $i\in\left[ 1, N \right]$. Assume the noise is $e$.
-So the mixed utterance $U$ is as equation~\ref{eq:mixed}.
+Assume there are $N$ speakers talking simultaneously, they are called $s_1, s_2, \dots s_N$.
+The waveform of speech utterance for each speaker is $U_i\left( t \right)$ while $i\in\left[ 1, N \right]$.
+Assume the noise is $e\left( t \right)$.
+So the mixed utterance $X\left( t \right)$ is as equation~\ref{eq:mixed}.
 \begin{equation}
-    U = \sum\limits_{i=1}^N U_i + e\label{eq:mixed}
+    X\left( t \right) = \sum\limits_{i=1}^N U_i\left( t \right) + e\left( t \right)
+    \label{eq:mixed}
 \end{equation}
-For the mission of Target Speaker Separation (TSS) Task. Assume we only need to extract the voice of speaker $s_n$ and we have the reference utterance from $s_n$, denoted as $R_n$.
-The task is given $U = \sum\limits_{i=1}^N U_i + e$ and $R_n$, we need to get $U_n$.
+For the mission of Target Speaker Separation (TSS) Task.
+Assume we only need to extract the voice of speaker $s_n$ from $X\left( t \right)$ and we have the reference utterance from $s_n$, denoted as $R_n$.
+The task is given $X\left( t \right) = \sum\limits_{i=1}^N U_i\left( t \right) + e\left( t \right)$ and $R_n$, we need to get $U_n\left( t \right)$.
+
+\subsection{Metrics}\label{subsec:metrics}
+
+Using meaningful metrics to define the performance of the separation system is important.
+
+\begin{itemize}
+    \item source-to-distortion ratio (SDR)
+
+    SDR is defined in~\cite{performance_measurement}, and is as equation~\ref{eq:sdr}.
+    \begin{equation}
+        \text{SDR} \coloneqq 10\log_{10}\frac{\| s_{\text{target}} \|^2}{\| e_{\text{interf}} + e_{\text{noise}} + e_{\text{artif}} \|^2}
+        \label{eq:sdr}
+    \end{equation}
+
+    \item scale-invariant source-to-noise ratio (SI-SNR)
+
+    SI-SNR is proposed in~\cite{tasnet}, and is as equation~\ref{eq:si-snr}.
+    \begin{equation}
+        \begin{aligned}
+            s_{\text{target}} &= \frac{\left< \hat{s}, s \right>s}{\| s \|^2} \\
+            e_{\text{noise}} &= \hat{s} - s_{\text{target}} \\
+            \text{SI-SNR} &\coloneqq 10\log_{10}\frac{\| s_{\text{target}} \|^2}{\| e_{\text{noise}} \|^2}
+        \end{aligned}\label{eq:si-snr}
+    \end{equation}
+\end{itemize}
+
+\subsection{Methodology}\label{subsec:methodology}

### 2022-04-24 background.tex
Update metric description
Add waveform example

@@
 \end{equation}
+One waveform example is as figure~\ref{fig:waveform}.
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=0.8\textwidth]{img/waveform}
+    \caption{One example of how waveform looks like}
+    \label{fig:waveform}
+\end{figure}
+
 For the mission of Target Speaker Separation (TSS) Task.
@@
 Using meaningful metrics to define the performance of the separation system is important.
+To evaluate the performance of separation system, the metric should be designed to objectively represent ``how good'' the extracted waveform is.
+The idea of projecting one high dimensional vector onto another high dimensional vector comes in mind.
 

### 2022-04-24 background.tex
Update methodology and add references

@@
 \subsection{Methodology}\label{subsec:methodology}
+
+To extract target speaker's voice from the mixed utterance, we first need to extract the information of the target speaker.
+One common way is to use a vector to represent target speaker's information, and we call it the speaker embedding.
+There are many ways and many different speaker embeddings, such as i-vector in~\cite{i-vector}, a speaker embedding based on end-to-end neural network in~\cite{deep_speaker}, x-vector in~\cite{x-vector}, d-vector in~\cite{d-vector}.
+
+\subsubsection{Frequency-domain methods}
+
+\subsubsection{Time-domain methods}

### 2022-04-25 background.tex
Update speaker embedding citation
Add spec example

@@
 There are many ways and many different speaker embeddings, such as i-vector in~\cite{i-vector}, a speaker embedding based on end-to-end neural network in~\cite{deep_speaker}, x-vector in~\cite{x-vector}, d-vector in~\cite{d-vector}.
+As Transformer architecture~\cite{attention} being existed, there are some Transformer encoder based speaker embeddings happen, such as s-vector in~\cite{s-vector}.
+
+After extracting the speaker embedding, there are basically two different ways to do the separation task, one is frequency-domain methods, another is time-domain methods.
 
@@
 
+For the frequency-domain methods, the central part is processing the spectrogram. Here gives an example in figure~\ref{fig:spec_exp}.
+\begin{figure}
+    \centering
+    \stackunder[5pt]{\includegraphics[width=0.9\linewidth]{img/spec_exp_mix}}{(a)}
+    \stackunder[5pt]{\includegraphics[width=0.9\linewidth]{img/spec_exp_tar}}{(b)}
+    \stackunder[5pt]{\includegraphics[width=0.9\linewidth]{img/spec_exp_est}}{(c)}
+    \caption{Spectrogram example of 1650-167613-0006.
+(a) Spectrogram of the mixed utterance; (b) Spectrogram of the target speaker utterance; (c) Spectrogram of the estimated target speaker utterance.
+}
+    \label{fig:spec_exp}
+\end{figure}
+
 \subsubsection{Time-domain methods}

### 2022-04-25 background.tex
Update freq-domain methods description

@@
 One common way is to use a vector to represent target speaker's information, and we call it the speaker embedding.
-There are many ways and many different speaker embeddings, such as i-vector in~\cite{i-vector}, a speaker embedding based on end-to-end neural network in~\cite{deep_speaker}, x-vector in~\cite{x-vector}, d-vector in~\cite{d-vector}.
+There are many ways and many different speaker embeddings, such as i-vector based on simple factor analysis in~\cite{i-vector}, a speaker embedding based on end-to-end neural network in~\cite{deep_speaker}, x-vector in~\cite{x-vector}, d-vector in~\cite{d-vector}.
 As Transformer architecture~\cite{attention} being existed, there are some Transformer encoder based speaker embeddings happen, such as s-vector in~\cite{s-vector}.
@@
 
-For the frequency-domain methods, the central part is processing the spectrogram. Here gives an example in figure~\ref{fig:spec_exp}.
+For the frequency-domain methods, the central part is processing the magnitude spectrogram. Here gives an example in figure~\ref{fig:spec_exp}.
 \begin{figure}
@@
     \stackunder[5pt]{\includegraphics[width=0.9\linewidth]{img/spec_exp_est}}{(c)}
-    \caption{Spectrogram example of 1650-167613-0006.
-(a) Spectrogram of the mixed utterance; (b) Spectrogram of the target speaker utterance; (c) Spectrogram of the estimated target speaker utterance.
+    \caption{Magnitude spectrogram example of 1650-167613-0006.
+(a) Magnitude spectrogram of the mixed utterance; (b) Magnitude spectrogram of the target speaker utterance; (c) Magnitude spectrogram of the estimated target speaker utterance.
 }
@@
 
+For each utterance, by doing Fourier transform, it can be converted into magnitude spectrogram and phase spectrogram.
+For the frequency-domain methods, the central part is to mask the magnitude spectrogram.
+In (a), it is the magnitude spectrogram of the mixed utterance which contains two speakers, and (b) is the magnitude spectrogram of the target speaker's utterance.
+The goal is by given (a) and the target speaker's reference audio, we want to get (b).
+(c) is our system's estimated magnitude spectrogram of target speaker's utterance, and it is very visually similar to (b).
+For the frequency-domain methods, the mask is estimated, and dot multiplied to the mixed magnitude spectrogram for getting the estimated one.
+The whole process can be described in figure~\ref{fig:sep_process}.
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=0.8\textwidth]{img/sep_process}
+    \caption{Frequency-domain methods general description}
+    \label{fig:sep_process}
+\end{figure}
+
 \subsubsection{Time-domain methods}

### 2022-04-25 background.tex
Add deep clustering and PIT

@@
 
+There are many methods using this framework, such as deep clustering~\cite{deep_clustering}, which trains a deep network to produce spectrogram embeddings.
+The estimated mask is binary, and the projection process is achieved by the deep neural network, and the objective function it trains is as equation~\ref{eq:deep_clustering}.
+\begin{equation}
+    C_Y\left( V \right) = \| VV^T - YY^T \|_F^2
+    \label{eq:deep_clustering}
+\end{equation}
+
+Also, permutation invariant training (PIT) in~\cite{pitch_aware}, which is widely used in blind speaker separation.
+One big problem of speaker independent speech separation is the permutation of the output of the network.
+PIT solves this problem, which outputs all the permutations and using the smallest mean squared error (MSE) as the optimization goal.
+PIT structure is as figure~\ref{fig:PIT_structure}.
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=0.8\textwidth]{img/PIT_structure}
+    \caption{Permutation invariant training structure}
+    \label{fig:PIT_structure}
+\end{figure}
+
 \subsubsection{Time-domain methods}

### 2022-04-25 background.tex
Add uPIT

@@
 
-Also, permutation invariant training (PIT) in~\cite{pitch_aware}, which is widely used in blind speaker separation.
+Also, permutation invariant training (PIT) in~\cite{PIT}, which is widely used in blind speaker separation.
 One big problem of speaker independent speech separation is the permutation of the output of the network.
@@
 PIT structure is as figure~\ref{fig:PIT_structure}.
+To better solve the issue of tracking the speaking person, one utterance-level algorithm uPIT in~\cite{uPIT} is proposed.
 \begin{figure}[!htbp]

### 2022-04-25 background.tex
Add DEF-DL description

@@
 
+To better solve the disadvantages of deep clustering, a new deep embedding clustering based algorithm DEF-DL~\cite{DEF-DL} is proposed.
+DEF-DL uses supervised network to replace of K-means clustering algorithm, and use this feature as the input of uPIT network to separate speech.
+The whole structure is as figure~\ref{fig:def_dl_structure}.
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=0.6\textwidth]{img/DEF-DL_structure}
+    \caption{DEF-DL structure}
+    \label{fig:def_dl_structure}
+\end{figure}
+
 \subsubsection{Time-domain methods}

### 2022-04-25 background.tex
Update voicefilter description

@@
     \includegraphics[width=0.8\textwidth]{img/PIT_structure}
-    \caption{Permutation invariant training structure}
+    \caption{Permutation invariant training structure~\cite{PIT}}
     \label{fig:PIT_structure}
@@
 To better solve the disadvantages of deep clustering, a new deep embedding clustering based algorithm DEF-DL~\cite{DEF-DL} is proposed.
-DEF-DL uses supervised network to replace of K-means clustering algorithm, and use this feature as the input of uPIT network to separate speech.
+DEF-DL uses supervised network to replace K-means clustering algorithm, and use this feature as the input of uPIT network to separate speech.
 The whole structure is as figure~\ref{fig:def_dl_structure}.
@@
     \includegraphics[width=0.6\textwidth]{img/DEF-DL_structure}
-    \caption{DEF-DL structure}
+    \caption{DEF-DL structure~\cite{DEF-DL}}
     \label{fig:def_dl_structure}
 \end{figure}
+For the target speaker separation, one classic structure is speaker encoder, speech encoder, separator, decoder framework, as shown in figure~\ref{fig:enc_sep_doc_arc}.
+
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=0.7\textwidth]{img/voicefilter_struct}
+    \caption{VoiceFilter structure~\cite{voicefilter}}
+    \label{fig:voicefilter_struct}
+\end{figure}
+
+One example is VoiceFilter~\cite{voicefilter}, the structure is shown in figure~\ref{fig:voicefilter_struct}.
+The speaker encoder is trained separately to get the speaker embedding.
+For each iteration of training, the noisy audio, clean audio and reference audio are given.
+Operating Short-time Fourier transform (STFT) to both noisy audio and clean audio to get the magnitude spectrogram and phase spectrogram.
+The magnitude spectrogram of the noisy audio is fed into the separator, for VoiceFilter, it is Convolutional Neural Network (CNN), Long short-term memory (LSTM)~\cite{LSTM} and fully-connected layer.
+After the separator predicting the mask, dot multiplication is applied to the input magnitude spectrogram to get the predicted masked magnitude spectrogram.
+Last, applying inverse STFT to the masked magnitude spectrogram and the original phase spectrogram to get the enhanced audio.
+The training loss of the network is mean squared error (MSE) between the masked magnitude spectrogram and the clean spectrogram from the clean audio.
 

### 2022-04-25 background.tex
Add two citations in frequency-domain methods

@@
 After the separator predicting the mask, dot multiplication is applied to the input magnitude spectrogram to get the predicted masked magnitude spectrogram.
-Last, applying inverse STFT to the masked magnitude spectrogram and the original phase spectrogram to get the enhanced audio.
+Last, applying inverse STFT (iSTFT) to the masked magnitude spectrogram and the original phase spectrogram to get the enhanced audio.
 The training loss of the network is mean squared error (MSE) between the masked magnitude spectrogram and the clean spectrogram from the clean audio.
 
+However by applying iSTFT on the masked magnitude spectrogram and the original phase spectrogram to get the enhanced audio may have the effect on the performance since the phase spectrogram is not processed.
+There are some methods that can reconstruct phase information, such is WA-MISI in~\cite{WA-MISI} and Deep CASA in~\cite{Deep_CASA}.
+
 \subsubsection{Time-domain methods}

### 2022-04-25 background.tex
Update conv tasnet

@@
 Last, applying inverse STFT (iSTFT) to the masked magnitude spectrogram and the original phase spectrogram to get the enhanced audio.
-The training loss of the network is mean squared error (MSE) between the masked magnitude spectrogram and the clean spectrogram from the clean audio.
+The training loss of the network is mean squared error (MSE) between the masked magnitude spectrogram and the clean spectrogram from the clean audio, which is also very common in the frequency-domain methods.
 
@@
 \subsubsection{Time-domain methods}
+
+To better solve the problem of the phase information is not matched to the masked spectrogram, many time-domain methods existed.
+For the time-domain methods, the input and output are not magnitude spectrogram anymore.
+These methods directly process the waveform and output the waveform.
+Since the waveform contains both magnitude and phase information, the issue of mis-matching phase can be solved.
+There are some outstanding works of time-domain methods, such as Conv-TasNet~\cite{conv_tasnet}, which has three main modules: encoder, separator and decoder.
+For the encoder, it uses 1-dimensional convolutional layer to replace STFT to encode the waveform, which forces the network to learn the parameters.
+For the separator, it was fed the feature from the encoder and output the mask which is very similar to the frequency-domain methods.
+Dot multiplication is applied to the mask and the output feature from the encoder.
+Last but not least, the decoder which is a transpose 1-dimensional convolutional layer which takes the output from the separator to the audio signal.
+Conv-TasNet directly use Si-SNR~\ref{eq:si-snr} as the training loss, which can improve the performance and solve the issue of the mismatching phase information.

### 2022-04-25 acknowledgements.tex
Update acknowledgements

@@
 
-Last but not least, I want to thank all the members in my family. They have supported me for all my life.
+I also want to thank all the members in my family. They have supported me for all my life and they will always have my back.
+
+Next I want to thank Yunan Huang, my girlfriend. She and I had a long-distance relationship for the whole undergraduate life, which is very tough.
+She loves me, knows me, understands me and always inspires me when I met difficulties.
+
+Last but not least, I want to thank my friends, including Jiasheng Zhu, Ziang Zhou, Jiyang Tang, Mamabean and Bababean and all the other friends I met at DKU.
+Our invaluable friendship makes me a better person.

### 2022-04-25 acknowledgements.tex
check grammar of acknowledgements

--- 2022-04-23 acknowledgements.tex
@@
 \section{ACKNOWLEDGEMENTS}\label{sec:acknowledgements}
-First and foremost, I would like to thank my research mentor Professor Ming Li who provided huge help to me in the past three years.
-I first met the professor was in the class of CS 101.
-Later on I applied to join Prof. Ming Li's Speech and Multimodal Intelligent Information Processing (SMIIP) Lab during the summer of my freshman year.
+First and foremost, I would like to thank my research mentor Professor Ming Li who provided huge help to me over the past three years.
+I first met the professor in the class CS 101 Introduction to Computer Science.
+Later on, I applied to join Prof. Ming Li's Speech and Multimodal Intelligent Information Processing (SMIIP) Lab during the summer of my freshman year.
 From that time, under the guidance and resources provided by the professor, I started my research in the field of speech analysis technology and speech separation.
+Without the professor's invaluable guidance, my research in the field of speech analysis technology and this signature work cannot happen.
+
+Second, I want to thank my senior schoolfellows Yuanyuan Bao, Yanze Xu, Bang Zeng, Zhan Jin, and all the other members in the same lab.
+They provided a lot of help on my path of doing research in the target speaker separation (TSS) field.
+It is their help that I can move forward smoothly and I learned a lot of skills from them.
+
+Third, I want to thank Summer Research Scholar (SRS) program provided by Duke Kunshan University.
+This program provided research funds during the summer of my junior year.
+
+I also want to thank all the members of my family. They have supported me all my life and they will always have my back.
+
+Next, I want to thank Yunan Huang, my girlfriend. She and I had a long-distance relationship for our whole undergraduate life, which is very tough.
+She loves me, knows me, understands me, and always inspires me when I met difficulties.
+
+Last but not least, I want to thank my friends, including Jiasheng Zhu, Ziang Zhou, Jiyang Tang, Mamabean and Bababean, and all the other friends I met at DKU.
+Our invaluable friendship makes me a better person.

### 2022-04-25 background.tex
ADD DPRNN
Check grammar of background

@@
 
-In this section, we give a detailed background about what is target speaker separation (TSS) task, what kinds of metrics can be used to define the performance, what kinds of techniques existed can be used to do TSS task.
+In this section, we give a detailed background about what is target speaker separation (TSS) task, what kinds of metrics can be used to define the performance and what kinds of techniques existed can be used to do TSS task.
 
@@
     \includegraphics[width=0.8\textwidth]{img/waveform}
-    \caption{One example of how waveform looks like}
+    \caption{One example of how the waveform looks like}
     \label{fig:waveform}
@@
 
-For the mission of Target Speaker Separation (TSS) Task.
+For the mission of the Target Speaker Separation (TSS) Task.
 Assume we only need to extract the voice of speaker $s_n$ from $X\left( t \right)$ and we have the reference utterance from $s_n$, denoted as $R_n$.
@@
 Using meaningful metrics to define the performance of the separation system is important.
-To evaluate the performance of separation system, the metric should be designed to objectively represent ``how good'' the extracted waveform is.
-The idea of projecting one high dimensional vector onto another high dimensional vector comes in mind.
+To evaluate the performance of the separation system, the metric should be designed to objectively represent ``how good'' the extracted waveform is.
+The idea of projecting one high dimensional vector onto another high dimensional vector comes to mind.
 
@@
 
-To extract target speaker's voice from the mixed utterance, we first need to extract the information of the target speaker.
-One common way is to use a vector to represent target speaker's information, and we call it the speaker embedding.
+To extract the target speaker's voice from the mixed utterance, we first need to extract the information of the target speaker.
+One common way is to use a vector to represent the target speaker's information, and we call it the speaker embedding.
 There are many ways and many different speaker embeddings, such as i-vector based on simple factor analysis in~\cite{i-vector}, a speaker embedding based on end-to-end neural network in~\cite{deep_speaker}, x-vector in~\cite{x-vector}, d-vector in~\cite{d-vector}.
@@
 
-After extracting the speaker embedding, there are basically two different ways to do the separation task, one is frequency-domain methods, another is time-domain methods.
+After extracting the speaker embedding, there are basically two different ways to do the separation task, one is frequency-domain methods, and another is time-domain methods.
 
@@
 In (a), it is the magnitude spectrogram of the mixed utterance which contains two speakers, and (b) is the magnitude spectrogram of the target speaker's utterance.
-The goal is by given (a) and the target speaker's reference audio, we want to get (b).
-(c) is our system's estimated magnitude spectrogram of target speaker's utterance, and it is very visually similar to (b).
-For the frequency-domain methods, the mask is estimated, and dot multiplied to the mixed magnitude spectrogram for getting the estimated one.
+The goal is by giving (a) and the target speaker's reference audio, we want to get (b).
+(c) is our system's estimated magnitude spectrogram of the target speaker's utterance, and it is very visually similar to (b).
+For the frequency-domain methods, the mask is estimated, and is dot-multiplied to the mixed magnitude spectrogram for getting the estimated one.
 The whole process can be described in figure~\ref{fig:sep_process}.
@@
 
-Also, permutation invariant training (PIT) in~\cite{PIT}, which is widely used in blind speaker separation.
-One big problem of speaker independent speech separation is the permutation of the output of the network.
+Also, permutation invariant training (PIT) in~\cite{PIT} is widely used in blind speaker separation.
+One big problem of speaker-independent speech separation is the permutation of the output of the network.
 PIT solves this problem, which outputs all the permutations and using the smallest mean squared error (MSE) as the optimization goal.
@@
 To better solve the disadvantages of deep clustering, a new deep embedding clustering based algorithm DEF-DL~\cite{DEF-DL} is proposed.
-DEF-DL uses supervised network to replace K-means clustering algorithm, and use this feature as the input of uPIT network to separate speech.
+DEF-DL uses a supervised network to replace K-means clustering algorithm, and uses this feature as the input of uPIT network to separate speech.
 The whole structure is as figure~\ref{fig:def_dl_structure}.
@@
 The speaker encoder is trained separately to get the speaker embedding.
-For each iteration of training, the noisy audio, clean audio and reference audio are given.
+For each iteration of training, the noisy audio, clean audio, and reference audio are given.
 Operating Short-time Fourier transform (STFT) to both noisy audio and clean audio to get the magnitude spectrogram and phase spectrogram.
 The magnitude spectrogram of the noisy audio is fed into the separator, for VoiceFilter, it is Convolutional Neural Network (CNN), Long short-term memory (LSTM)~\cite{LSTM} and fully-connected layer.
-After the separator predicting the mask, dot multiplication is applied to the input magnitude spectrogram to get the predicted masked magnitude spectrogram.
+After the separator predicts the mask, dot multiplication is applied to the input magnitude spectrogram to get the predicted masked magnitude spectrogram.
 Last, applying inverse STFT (iSTFT) to the masked magnitude spectrogram and the original phase spectrogram to get the enhanced audio.
@@
 
-However by applying iSTFT on the masked magnitude spectrogram and the original phase spectrogram to get the enhanced audio may have the effect on the performance since the phase spectrogram is not processed.
+However, applying iSTFT on the masked magnitude spectrogram and the original phase spectrogram to get the enhanced audio may affect the performance since the phase spectrogram is not processed.
 There are some methods that can reconstruct phase information, such is WA-MISI in~\cite{WA-MISI} and Deep CASA in~\cite{Deep_CASA}.
@@
 These methods directly process the waveform and output the waveform.
-Since the waveform contains both magnitude and phase information, the issue of mis-matching phase can be solved.
+Since the waveform contains both magnitude and phase information, the issue of mismatching phase can be solved.
 There are some outstanding works of time-domain methods, such as Conv-TasNet~\cite{conv_tasnet}, which has three main modules: encoder, separator and decoder.
@@
 Last but not least, the decoder which is a transpose 1-dimensional convolutional layer which takes the output from the separator to the audio signal.
-Conv-TasNet directly use Si-SNR~\ref{eq:si-snr} as the training loss, which can improve the performance and solve the issue of the mismatching phase information.
+Conv-TasNet directly uses Si-SNR~\ref{eq:si-snr} as the training loss, which can improve the performance and solve the issue of the mismatching phase information.
+However Conv-TasNet can only focus on the segmented length of the audio, it cannot focus on the whole utterance.
+A new system which is also a time-domain method called Dual-Path RNN (DPRNN) is proposed in~\cite{dprnn}, which can focus on the whole utterance and thus improve the performance.
